---
title: "Contraception Service Opt In Weekly update"
author: "As on `r Sys.Date()`"

output:
  beamer_presentation:
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
---


```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(readr)
library(writexl)
library(xlsx)
library(ggpubr)
library(stringr)
library(scales)
library(readxl)
library(textclean)
library(grid)
library(gridExtra)
library(knitr)

source("../OC_optin.R")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## National view
```{r  National_OptedIn, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
plot_OC_national()
```

* As on **`r get_last_OC()`** at national level, **`r get_total_OC()`** contractors (**`r get_total_prec_OC()`**% of all non-DAC contractors) have opted in to Contraception Service. These include pharmacies newly signed up since 1st December and opted in by default. 


## Regional summary table
```{r  Regional_OptedIn, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_2())
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In London Region
```{r  ICB_OptedIn_lon, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("London"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In South East Region
```{r  ICB_OptedIn_se, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("South East"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In South West Region
```{r  ICB_OptedIn_SW, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("South West"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In Midlands Region
```{r  ICB_OptedIn_mid, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("Midlands"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In East of England Region
```{r  ICB_OptedIn_eoe, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("East of England"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In North West Region
```{r  ICB_OptedIn_NW, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("North West"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICBs In LNorth East and Yorkshire Region
```{r  ICB_OptedIn_ney, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
kable(get_OC_table_3("North East And Yorkshire"))
```

* Cumulative total contractors opted in to Contraception service as on **`r get_last_OC()`**)

## ICB level map
```{r  ICB_map, echo = FALSE, warning = FALSE, fig.height=5, message = FALSE}
map_OC_icb(interactive_mode = FALSE)
```
