---
title: "Pharmacy First Opt In Weekly Update"

date: "Report date: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [theme.css, nhsr-fonts.css]
    self_contained: true
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(DBI)
library(readr)
library(writexl)
library(xlsx)
library(ggpubr)
library(stringr)
library(scales)
library(readxl)
library(textclean)
library(grid)
library(gridExtra)
library(htmlwidgets)
library(downloadthis)
library(knitr)
library(kableExtra)
library(reactable)

source("../01 Pharm1st_opt_in.R")


knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#avoid standard form
options(scipen=999)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```
#### NOTE 

This pack is updated weekly. Opt-In and registration data for all services included in this pack are provided by BSA's MYS team. 

DAC contractors have been excluded from any analysis in this pack. 

---

name: National

### National View

```{r  echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[Overview]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=4, fig.align='center'}
plot_ph1st_national()
```

* As on **`r get_last()`** at national level, **`r get_total()`** contractors (**`r get_total_prec()`**% of all non-DAC contractors) have opted in to Pharmacy First Service. For comparison, **`r get_CPCS_valid()`** contractors have signed up for CPCS since service launch. Contractors that had permanently closed or de-registered have been excluded using pharmaceutical list published on **`r get_pharmList_date()`**.
* As on **`r get_last_OC()`** at national level, **`r get_total_OC()`** contractors (**`r get_total_prec_OC()`**% of all non-DAC contractors) have opted in to Contraception Service. These include pharmacies newly signed up since 1st December and opted in automatically. 
* As on **`r get_last_BP()`** at national level, **`r get_BP_totalReg()`** contractors had registered to provide BP check service, but **`r get_BP_invalid()`** of them have permanently closed, changed ownership or consolidated with other pharmacies.  Out of all **`r get_BP_totalReg()-get_BP_invalid()`** valid registrations, **`r get_BP_newReg()`** contractors were new opt-ins since 1st December 2023. 

]
.panel[.panel-name[Summary table (National)]
<font size="1">
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}

Ph1st_national%>%
  download_this(
    output_name = "national_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r table_national,echo=FALSE,warning=FALSE, fig.width=15, fig.height=10,fig.retina=1, dpi=50,fig.align='center'}

reactable(
  Ph1st_national,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)

```

]
]
---

name: Regional
### Regional View

```{r  echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[
.panel[.panel-name[Regional Overview]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_ph1st_regional()
```


]
.panel[.panel-name[Summary table (Regional)]
<font size="1">
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}

ph1st_regional %>%
  download_this(
    output_name = "Regional_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r table_regional,echo=FALSE,warning=FALSE, fig.width=15, fig.height=10,fig.retina=1, dpi=50,fig.align='center'}

reactable(
  ph1st_regional,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

]
]
---

name: ICB
### ICB View

```{r  echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("London")

data %>%
  download_this(
    output_name = "London_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("South East")

data %>%
  download_this(
    output_name = "SE_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("South West")

data %>%
  download_this(
    output_name = "SW_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("Midlands")

data %>%
  download_this(
    output_name = "Midlands_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("East Of England")

data %>%
  download_this(
    output_name = "EoE_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("North West")

data %>%
  download_this(
    output_name = "NW_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=15, fig.height=10}
data<-get_pha1st_table_3("North East And Yorkshire")

data %>%
  download_this(
    output_name = "NEY_opt_in",
    output_extension = ".xlsx",
    button_label = "Download Table",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save")
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=16, fig.height=5, fig.align='center'}
reactable(
  data,
  filterable = FALSE,
  resizable = TRUE,
  defaultPageSize =7,
  defaultExpanded = FALSE,
  paginateSubRows = TRUE,
  height=400,
  highlight = TRUE)
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**

]
]
---

name: Maps
### ICB heatmaps

```{r  echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[Pharmacy First Opt-in]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
library(sf)
map_pha1st_icb(interactive_mode = FALSE, serv="Pharmacy First")
```

]
.panel[.panel-name[CPCS signups not opted in Pharmacy First]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
library(sf)
map_pha1st_icb(interactive_mode = FALSE, serv="CompareCPCS")
```

]
.panel[.panel-name[Contraception Opt-in]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
library(sf)
map_pha1st_icb(interactive_mode = FALSE, serv="Contraception")
```

]
]

---
