---
title: "Pharmacy First Service Weekly update"
author: "As on `r Sys.Date()`"

output:
  beamer_presentation:
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
---


```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(readr)
library(writexl)
library(xlsx)
library(ggpubr)
library(stringr)
library(scales)
library(readxl)
library(textclean)
library(grid)
library(gridExtra)
library(knitr)

source("../01 Pharm1st_opt_in.R")
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## National view
```{r  National_OptedIn, echo = FALSE, warning = FALSE, fig.height=3, message = FALSE}
plot_ph1st_national()
```

* As on **`r get_last()`** at national level, **`r get_total()`** contractors (**`r get_total_prec()`**% of all non-DAC contractors) have opted in to Pharmacy First Service.
* As on **`r get_last_OC()`** at national level, **`r get_total_OC()`** contractors (**`r get_total_prec_OC()`**% of all non-DAC contractors) have opted in to Contraception Service. These include pharmacies newly signed up since 1st December and opted in automatically. 
* As on **`r get_last_BP()`** at national level, **`r get_BP_totalReg()`** contractors had registered to provide BP check service, but **`r get_BP_invalid()`** of them have permanently closed, changed ownership or consolidated with other pharmacies according to pharmaceutical list published on **`r get_pharmList_date()`**.  Out of all **`r get_BP_totalReg()-get_BP_invalid()`** valid registrations, **`r get_BP_newReg()`** contractors were new opt-ins since 1st December 2023. 

## Regional summary table
```{r  Regional_OptedIn, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_2())    
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In London Region
```{r  ICB_OptedIn_lon, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("London"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In South East Region
```{r  ICB_OptedIn_se, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("South East"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In South West Region
```{r  ICB_OptedIn_SW, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("South West"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In Midlands Region
```{r  ICB_OptedIn_mid, echo = FALSE, warning = FALSE, fig.height=3.8, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("Midlands")[c(1,2,3,4,5),])
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)
* The rest of ICBS in Midlands region are listed in the next page. 

## ICBs In Midlands Region - cont.
```{r  ICB_OptedIn_mid2, echo = FALSE, warning = FALSE, fig.height=3.8, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("Midlands")[c(6,7,8,9,10,11),])
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In East of England Region
```{r  ICB_OptedIn_eoe, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("East Of England"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In North West Region
```{r  ICB_OptedIn_NW, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("North West"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICBs In North East and Yorkshire Region
```{r  ICB_OptedIn_ney, echo = FALSE, warning = FALSE, fig.height=4, message = FALSE}
library(knitr)
knitr::kable(get_pha1st_table_3("North East And Yorkshire"))
```

* Cumulative total contractors opted in to Pharmacy First service as on **`r get_last()`**)

## ICB level map for Pharmacy First Opt-in
```{r  ICB_map_ph1st, echo = FALSE, warning = FALSE, fig.height=5, message = FALSE}
library(sf) 
map_pha1st_icb(interactive_mode = FALSE, serv="Pharmacy First")
```


## ICB level map for Contraception Opt-in
```{r  ICB_map_contrac, echo = FALSE, warning = FALSE, fig.height=5, message = FALSE}
map_pha1st_icb(interactive_mode = FALSE, serv="Contraception")
```
